\textbf{A Serious Game for Aiding the Screening of Dyslexia in Children and Young Adults}

### 2014-06-24 article.tex
Add Evaluation Introduction

\section{Evaluation}
\subsection{Method}
\subsubsection{Design}
\subsubsection{Apparatus and Materials}
\subsubsection{Participants}
\subsubsection{Procedure}
\subsection{Results}
\subsection{Discussion}
\section{Conclusions}
\subsection{Further Work}
\bibliography{references}
\bibliographystyle{IEEEtran}
\section{Appendix}
\end{document}

>>>>

\section{Evaluation}
An experiment aiming to test the games effectiveness as a screening test, and its overall usability, has be designed.

The games purpose, as previously explained, is to screen children and young adults for dyslexia, in order to ascertain whether this is possible a study must be conducted. In this study participants both with and without dyslexia will play the game and performance metrics will be collected and analysed to determine if there are any significant differences between the metrics achieved by the two groups. If differences are found then, in the future, new users could be classified into one of the two groups based on the metrics they attain.

The null hypothesis for this study is therefore:
\begin{center}
\textbf{NH.1:} \textit{There is no observable difference between the game metrics achieved by those with dyslexia and by those without}
\end{center}

In addition, the usability of the game can be explored as part of the study, in order to determine whether the design and structure of the game meets user expectations. When considering the usability of the game, a questionnaire can be used to gain insight into the users opinion on game aspects such as controls, theme, duration, and difficulty. The results of this questionnaire can be used to help guide future development and alterations to the game design and structure.

\subsection{Method}
\subsubsection{Design}
\subsubsection{Apparatus and Materials}
\subsubsection{Participants}
\subsubsection{Procedure}
\subsection{Results}
\subsection{Discussion}
\section{Conclusions}
\subsection{Further Work}
\bibliography{references}
\bibliographystyle{IEEEtran}
\section{Appendix}
\end{document}
